\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}

\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{John McAvoy}

\address{208 Abbey Lane, Logan Township, NJ 08085 \\ +18563572550 \\
\href{mailto:j-mcavoy@protonmail.com}{j-mcavoy@protonmail.com} \\
\href{http://j-mcavoy.gitlab.io}{j-mcavoy.gitlab.io}}

\address{
  \href{http://linkedin.com/in/john-mcavoy-8b888b183}{linkedin.com/in/john-mcavoy-8b888b183} \\
  \href{http://github.com/j-mcavoy}{github.com/j-mcavoy} \\
  \href{http://gitlab.com/j-mcavoy}{gitlab.com/j-mcavoy}
}
\begin{document}

\begin{rSection}{Education}

  {\bf Bachelor of Science, Electrical and Computer Engineering} \hfill
  {September 2015 - May 2020}
  \\
  Rowan University, Glassboro, NJ,  GPA:  3.658/4.000, Cum Laude, Rowan Scholars Program

\end{rSection}

%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNICAL SKILLS}

  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{0ex}} l }
    &
    %Altium
    %Apache $\vert$
    Bash $\vert$
    C $\vert$
    C++ $\vert$
    C\# $\vert$
    Docker $\vert$
    Elm $\vert$
    %HTML $\vert$
    Java $\vert$
    JavaScript $\vert$
    MATLAB $\vert$
    Node.js $\vert$
    PHP $\vert$
    Python $\vert$
    %React $\vert$
    Rust $\vert$
    %Solidworks $\vert$
    SQL $\vert$
    Swift $\vert$
    Verilog

    \\

    %           Interests&
    &
    Software Engineering,
    Linux Development,
    Full-stack Development,
    Embedded Systems,
    PCB Design,
    Product Engineering
    \\

  \end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{TECHNICAL PROJECTS}

  \begin{rSubsection}{Clean Room Environmental Chamber}{September 2019 - May
    2020}{Product Development Engineering Senior Clinic}{}
  \item A novel environmental chamber for the Rowan ECE clean room for storing
    solder paste and FR1 boards.
  \item Consulted with a client to create a project scope, WBS, requirements and
    specifications, high-level and low-level design.
  \item Electrical design consists of two ATmega644PA MCUs, Peltier element, and
    solenoid-controlled pneumatic system.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{A-Team Server}{January 2018 - May 2020}{A-Team, Server
    Administer / Full-Stack Developer}{}
  \item Linux server running a Rust back end, an
    Elm front end, and MySQL database in separate Docker containers.
  \item Hosts web applications for the Rowan Engineering department to track equipment
    loans, manage safety tests, and manage chemical inventories.
  \end{rSubsection}

  %------------------------------------------------

  %  \begin{rSubsection}{3D Printer Heated Filament Enclosure}{October 2019 - Present}{A-Team,
  %      Electrical Team Lead}{}
  %  \item Designed a custom heated filament enclosure for humidity sensitive 3D printing filament
  %  \item Integrates heater, temperature and humidity sensors, microcontroller and
  %    OLED user interface
  %  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Micromouse}{September 2018 - May 2020}{Rowan RAS}{}
  \item Maze solving robot for IEEE Micromouse competition. Won first place at
    IEEE Region 2 Student Activity Conference 2019.
  \item Consisted of a custom PCB, STM32F405 microcontroller, time of flight lidar
    distance sensors, 3D printed chassis, and embedded programming done in Rust.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{ProfHacks Website}{September 2018 - May 2020}{Rowan IEEE, Project Lead}{}
  \item Node.js-based website for Rowan IEEE's annual 24-hour Hackathon.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Autonomous Quadcopter}{September 2017 - December 2019}{Rowan
    RAS}{}
  \item Fully autonomous drone capable of navigating to waypoints, dropping a
    payload, and detecting targets with image recognition.
  \item Integrates a fight controller, SOC image processing, navigation sensors,
    a custom PCB, and a custom designed and manufactured aluminum frame. Capable
    of 1 hour of continuous flight.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Nanofiber Testing Apparatus}{January 2019 - May 2019}{Product Development Engineering Junior Clinic}{}
  \item A custom, heated tensile stretching apparatus for a client researching the strength of electrospun nanofibers.
  \item Consulted with a client to create a project scope, WBS, electrical
    design, and web-based user interface.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Augmented Reality Using Structured Light (ARSL)}{September
    2018 - December 2018}{ARSL Junior Clinic}{}
  \item A novel image processing method for creating an AR environment using projected light and a camera.
  \item Developed MATLAB, C++, and Android proof of concept applications using the
    ARSL method.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Lab Log Tool}{May 2018 - September 2018}{Harris Corporation, Project Lead}{}
  \item Developed a web application used by FAA employees to record lab logs, schedule lab times, and generate metrics.
  \item Back-end: Linux server running a Node.js web server, a Postfix mail server, and MySQL database.
  \end{rSubsection}

  %------------------------------------------------

  %\begin{rSubsection}{Rowan IEEE Website}{September 2017 - Present}{Rowan IEEE, Project Lead}{}
  %\item Node.js-based website for Rowan IEEE.
  %\end{rSubsection}
  %
  %------------------------------------------------

  %\begin{rSubsection}{8-bit Discrete Processor}{June 2017 - Present}{Rowan RAS, Project Lead}{}
  %\item An 8-bit processor constructed using only discrete IC logic gates.
  %\end{rSubsection}

  %------------------------------------------------

  %\begin{rSubsection}{Android Things Facial Recognition}{November 2017 - December 2017}{Google Hackathon}{}
  %\item Android IOT device that uses Google tensor flow to perform facial recognition to differentiate between users.
  %\end{rSubsection}

  %------------------------------------------------

  %\begin{rSubsection}{Smart Mirror}{December 2016 - February 2017}{Sophomore Clinic Project}{}
  %\item Raspberry Pi IOT mirror with facial recognition that displays time, weather, and news through a two-way mirror.
  %\end{rSubsection}


  %------------------------------------------------

  %\begin{rSubsection}{EEG Controller}{February 2017 - May 2017}{Sophomore Clinic Project}{}
  %\item Smart phone app that reads brain wave data from a custom wearable EGG.
  %\end{rSubsection}

\end{rSection}


%   EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{WORK EXPERIENCE / INTERNSHIPS} \itemsep -3pt
  \textbf{ECE Consultant, Rowan Apprentice Engineering Team (A-Team)} \hfill January 2018 - May 2020\\
  \textbf{Systems Engineering Intern, Innovative Defense Technologies (IDT)} \hfill May 2019 - August 2019\\
  \textbf{Datacom Intern, Harris Cooperation} \hfill May 2018 - September 2018\\
  \textbf{Chemical Engineering Lab Assistant, Rowan University} \hfill February 2017 - September 2017\\
  \textbf{Data Entry and QA Intern, Siegfried USA, LLC} \hfill June 2016 - September 2016\\
  \textbf{VR Development Intern, Virtual Reality Center, Rowan University} \hfill May 2016 - August 2016
\end{rSection}

\begin{rSection}{Professional Societies/Awards} \itemsep -3pt
  {\textbf{Rowan University IEEE Student Branch (Rowan IEEE)}, Service Chair,
  Webmaster, Student Member of the Month}\\
  {\textbf{Robotics and Automation Society Student Branch (Rowan RAS)}, Vice President, Project Coordinator Chair}\\
  {\textbf{Engineers Without Borders Student Branch}, Webmaster}
\end{rSection}

\end{document}
