\newcommand\skills{
  \textbf{Languages:}
  Bash,
  C,
  C++,
  C\#,
  CSS,
  HTML,
  Java,
  JavaScript,
  {\LaTeX},
  MATLAB,
  PHP,
  Python,
  Rust,
  SQL,
  Typescript
  \\
  \textbf{Web Frameworks:}
  Angular,
  Backbone,
  Django,
  Express.js,
  Elm,
  Flask,
  jQuery,
  Nuxt.js,
  React,
  Rocket,
  Spring,
  Vue.js
  \\
  \textbf{Dev Tools:}
  Ansible,
  Apache,
  Caddy,
  Docker,
  Electron,
  Git,
  Gradle,
  Kubernetes,
  Linux,
  Nginx,
  Travis CI,
  Yocto
}

\newcommand\projects{
  \begin{rSubsection}{Clean Room Environmental Chamber}{September 2019 - May
    2020}{Product Engineering Senior Clinic}{}
  \item Designed a novel environmental chamber for the Rowan ECE clean room for storing
    solder paste and FR1 boards.
  \item Consulted with a client to create a project scope, WBS, requirements and
    specifications, high-level and low-level design.
  \item Design consisted of two ATmega644PA MCUs, Peltier element, and
    solenoid-controlled pneumatic system.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{A-Team Server}{January 2018 - May 2020}{A-Team}{}
  \item Developed web applications for the Rowan Engineering department to track equipment
    loans, manage safety tests, and manage chemical inventories.
  \item Administered Linux server and configured a Rust webserver, Elm front
    end, and PostgreSQL Docker containers.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Micromouse}{September 2018 - May 2020}{Rowan RAS}{}
  \item Designed and programmed maze solving robot for IEEE Micromouse competition. Won first place at
    IEEE Region 2 Student Activity Conference 2019.
  \item Design consisted of a custom PCB, STM32F405 microcontroller, time of flight lidar
    distance sensors, 3D printed chassis.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{ProfHacks Website}{September 2018 - May 2020}{Rowan IEEE}{}
  \item Lead Agile development team to create website for Rowan IEEE's annual 24-hour Hackathon.
  \item Used Express.js framework, Mailgun, PostgreSQL database, and Gitlab CI/CD to test and deploy to Heroku.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Autonomous Quadcopter}{September 2017 - December 2019}{Rowan
    RAS}{}
  \item Lead software team to design a fully autonomous drone capable for the AUVSI SUAS competirion. Capable of 1
    hour of continuous flight, navigating to waypoints, dropping a
    payload, and detecting ground targets with image recognition.
  \item Integrates a fight controller, SOC image processing, GPS,
    and a custom designed aluminum frame.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Nanofiber Testing Apparatus}{January 2019 - May 2019}{Product Engineering Junior Clinic}{}
  \item Designed custom, heated tensile stretching apparatus for a client researching the strength of electrospun nanofibers.
  \item Consulted with a client to create a statement of work, work breakdown structure, electrical design, and user interface.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Augmented Reality Using Structured Light}{September
    2018 - December 2018}{ARSL Junior Clinic}{}
  \item Developed MATLAB, C++, and Android app applications to reconstruct a 3D mesh using the ARSL method.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Lab Log Tool}{May 2018 - September 2018}{Harris Corporation, Project Lead}{}
  \item Led development team to create a web application for FAA employees to record lab logs, schedule lab times, and view metrics.
  \item Administered Linux server running a Express.js web server, a Postfix mail server, and MySQL database.
  \end{rSubsection}

  }

  \newcommand\lifestory{
    I am a software and hardware generalist. I recently
    graduated with my B.S. in Electrical and Computer Engineering from Rowan
    University. During my time at Rowan, I've had extensive experience with
    software development, Linux server administration, embedded programming,
    and PCB design and fabrication. I've developed these skills in not only my courses,
    but also in doing extra-curricular projects in my professional societies, my internships, and my job working
    as a paid consultant for the Rowan Apprentice Engineering Team (A-Team). The
    A-Team is a company started by the ECE and ME technologists, which hires a
    select team of students as consultants to extend the skills we learn in
    the classroom to design and build products for the university, researchers, and
    clients outside of the university.

    During my time working on the A-Team, I was given special access to the university's
    mechanical projects lab, PCB assembly center, ECE resource center, as well as
    advanced training on all of the ECE instrumentation and ME machinery.  I
    also gained product development skills by consulting with clients, creating
    WBS and scopes of work, and practising interative design process on a team of both electrical and mechanical
    I have a deep passion for learning and sharing skills with a team and I believe that the resources at
    {\company} will give me the opportunity to apply my expertise and continue to learn
    new skills.
  }
