%\textbf{Web Frameworks:}
%Angular,
%Backbone,
%Express.js,
%Elm,
%Flask,
%React,
%Vue.js
\newcommand\skills{
  \textbf{Languages:}
  Bash,
  C,
  C++,
  C\#,
  CSS,
  HTML,
  Java,
  JavaScript,
  {\LaTeX},
  MATLAB,
  PHP,
  Python,
  Rust,
  SQL,
  Verilog
  \\
  \textbf{Dev Tools:}
  Ansible,
  Docker,
  Git,
  Kubernetes,
  Linux,
  Travis CI,
  Yocto
  \hspace{10}\textbf{CAD:}
  Altium,
  OrCAD,
  Solidworks
  \\
  \textbf{Instrumentation:}
  Oscilloscope,
  Multimeter,
  Logic Analyzer,
  Network Analyzer,
  Waveform Generator
  \\
  \textbf{Manufacturing:}
  3D Printing,
  Drill Press,
  Laser Cutter,
  Lathe,
  Mill,
  PCB Fabrication,
  Soldering,
  Waterjet
}

\newcommand\projects{
  \begin{rSubsection}{Clean Room Environmental Chamber}{September 2019 - May
    2020}{Product Engineering Senior Clinic}{}
  \item Designed a novel environmental chamber for the Rowan ECE clean room for storing
    solder paste and FR1 boards.
  \item Consulted with a client to create a project scope, WBS, requirements and
    specifications, high-level and low-level design.
  \item Design consists of two ATmega644PA MCUs, Peltier element, and
    solenoid-controlled pneumatic system.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{A-Team Server}{January 2018 - May 2020}{A-Team, Server
    Administer / Full-Stack Developer}{}
  \item Linux server running a Rust back end, an
    Elm front end, and MySQL database in separate Docker containers.
  \item Hosts web applications for the Rowan Engineering department to track equipment
    loans, manage safety tests, and manage chemical inventories.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Micromouse}{September 2018 - May 2020}{Rowan RAS}{}
  \item Maze solving robot for IEEE Micromouse competition. Won first place at
    IEEE Region 2 Student Activity Conference 2019.
  \item Consisted of a custom PCB, STM32F405 microcontroller, time of flight lidar
    distance sensors, 3D printed chassis, and Rust embedded programming.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{ProfHacks Website}{September 2018 - May 2020}{Rowan IEEE, Project Lead}{}
  \item Node.js-based website for Rowan IEEE's annual 24-hour Hackathon.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Autonomous Quadcopter}{September 2017 - December 2019}{Rowan
    RAS}{}
  \item Fully autonomous drone capable of navigating to waypoints, dropping a
    payload, and detecting targets with image recognition.
  \item Integrates a fight controller, SOC image processing, navigation sensors,
    a custom PCB, and a custom designed and manufactured aluminum frame. Capable
    of 1 hour of continuous flight.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Nanofiber Testing Apparatus}{January 2019 - May 2019}{Product Engineering Junior Clinic}{}
  \item A custom, heated tensile stretching apparatus for a client researching the strength of electrospun nanofibers.
  \item Consulted with a client to create a project scope, WBS, electrical
    design, and web-based user interface.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Augmented Reality Using Structured Light}{September
    2018 - December 2018}{ARSL Junior Clinic}{}
  \item Developed MATLAB, C++, and Android app proof of concept applications for the ARSL method.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Lab Log Tool}{May 2018 - September 2018}{Harris Corporation, Project Lead}{}
  \item Developed a web application used by FAA employees to record lab logs, schedule lab times, and generate metrics.
  \item Back-end: Linux server running a Node.js web server, a Postfix mail server, and MySQL database.
  \end{rSubsection}

  }

  \newcommand\lifestory{
    I am a software and hardware generalist. I recently
    graduated with my B.S. in Electrical and Computer Engineering from Rowan
    University. During my time at Rowan, I've had extensive experience with
    software development, Linux server administration, embedded programming,
    and PCB design and fabrication. I've developed these skills in not only my courses,
    but also in doing extra-curricular projects in my professional societies, my internships, and my job working
    as a paid consultant on the Rowan Apprentice Engineering Team (A-Team). The
    A-Team is a mentorship program and company started by the ECE and ME technologists, which hires a
    select team of students as consultants to extend the skills we learn in
    the classroom to design and build products for the university, researchers, and
    clients outside of the university.

    During my time working on the A-Team, I was given special access to the university's
    mechanical projects lab, PCB assembly center, ECE resource center, as well as
    advanced training on all of the ECE instrumentation and ME machinery.
    I have a deep passion for learning and sharing skills with a team and I believe that the resources at
    {\company} will give me the opportunity to apply my expertise and continue to learn
    new skills.
  }
